Supplement 1

### 2020-09-08 paper/supplement-1.Rmd
update missing data examples.

Data MCAR could occur if an Australian Football data collector was taking 
lunch during the third quarter of a match, resulting in data not being 
recorded for this time period. Data is MCAR, because the missings are 
not systematically related to other variables.

Data may be considered MAR is where missingness is related to some observed
data. Data MAR could arise if\... \^\^Rob's out on the full
example\--players who are injured are less likely to fill out wellness
surveys than those who are fully fit.\^\^.

>>>>

Data MCAR could occur if an Australian Football data collector was taking 
a lunch break during the third quarter of a match, resulting in data not being 
recorded for this time period. Data is MCAR, because the missings are 
not systematically related to other variables.

Data MAR are more likely to occur than data MCAR. Data MAR could arise if
a weighing scale used to measure players' pre- and post-match body mass 
produced more missing values when placed on soft carpet, rather than hard tiles. 
The scale may produce more missing values because of the soft surface. If 
surface type was recorded, data could be considered MAR, because the 
missingness is related to some observed data (i.e., surface), but not related 
to the value of the variable with the missing values itself.
